Constant Error Tolerance Computational Fuzzy Extractors

### 2014-02-04 trunk/constantRate/ConstCompFuzzExt.tex

\subsection{Obfuscation}
Our construction uses virtual black-box obfuscation of point functions.  This is the following family of functions:
\[
I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}.
\]
Here we present the virtual black-box definition of obfuscation.  See \secref{sec:obfuscation} for a more detailed introduction to obfuscation.  This definition is known to be achievable for point functions under various assumptions~\cite{canetti1997towards, wee2005obfuscating}.  We also need the obfuscation to be $\ell$-composable~(\defref{def:obf comp}).
\onote{if we need it, should put the def here not in the appendix. Also say that we need an AI definition}\onote{should discuss assumptions for composable AI point obfuscation. Here it make a lot of difference it we can get by with VGB}\onote{might be simpler to just define a set function instead of a point function and skip the composability stuff}
We present the notion of virtual black-box obfuscation with the weakening that the quality of the simulator is an arbitrarily small $1/\poly$ as all known point obfuscations satisfy this definition.

\begin{definition}~\cite{barak2001possibility, goldwasser2005impossibility}
\label{def:obf} Let $\mathcal{C}$ be a family of polynomial-size circuits.  A PPT algorithm $\mathcal{O}$ is an obfuscator for $\mathcal{C}$ with dependent \onote{remove dependent} auxiliary input if the following conditions are met:
\begin{enumerate}
\item \emph{Approximate Functionality:}  There exists a negligible function $\epsilon$ such that for every $n\in \mathbb{N}$, every circuit $C\in \mathcal{C}_n$, and every $x\in\zo^n$,
\[
\Pr[\mathcal{O}(C; r)(x) = C(x)] > 1-\epsilon(n),
\]
\bnote{We need a different name for the circuit, $C$ is our error-correcting code.}
where the probability is taken over the randomness $r$.  \emph{Almost exact functionality} is a stronger condition that requires $\mathcal{O}(C;r)\equiv C$ with overwhelming probability over the random coin tosses $r$.  Finally, if this probability always equals $1$, then $\mathcal{O}$ has \emph{exact functionality}. \onote{consider removing the notions you do not use}
\item \emph{Polynomial Slowdown:}  There exists a polynomial $\psi$ such that for every $n$, every circuit $C\in \mathcal{C}_n$, and every possible $r$, the circuit $\mathcal{O}(C; r)$ run-in time at most $\psi(n)$. \onote{this follows from the fact that O is PPT}
\item \emph{Virtual Black-box:}  For every PPT adversary $A$ and polynomial $\rho$, there exists a PPT simulator $S$ such that for all sufficiently large $n$, for all $C\in \mathcal{C}_n$, for all auxiliary inputs $z\in \zo^*$,
and for all binary predicates $\pi$,
\[
|\Pr[A(\mathcal{O}(C), z) = \pi(C, z)] - \Pr[S^C(1^n, z) = \pi(C, z)] | < \frac{1}{\rho(n)}
\]
where the first probability is taken over the coin tosses of $A$ and $\mathcal{O}$, and the second probability is taken over the coin tosses of $S$.  Furthermore, the runtime of $A$ and $S$ must be polynomial in the length of their first input.
\bnote{We never need to run our simulator so I think we can use virtual gray-box.}
\end{enumerate}
\end{definition}

>>>>

\subsection{Obfuscation}
Our construction uses obfuscation of point functions. This is the following family of functions:
\[
I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}.
\]
The notion of obfuscation required is virtual grey-box (VGB) introduced in \cite{bitansky2010strong}. This notion is weaker then the notion of virtual grey-box (\cite{barak2001possibility}) as it allows the simulator to run in unbounded time as long as it only makes polynomial number of oracle queries to the point function. In the following definition we also require that the obfuscation is composable and secure with respect to auxiliary input. Compassable auxiliary-input VGB obfuscators for point function are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Difﬁe Hellman assumption which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points.

\begin{definition}[$t$-composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
\label{def:obf} Let $\mathcal{I}$ be a family of polynomial-size circuits.  A PPT algorithm $\mathcal{O}$ is a $t$-composable VGB obfuscator for $\mathcal{I}$ with auxiliary-input if the following conditions are met:
\begin{enumerate}
\item \emph{Functionality:} for every $I \in \mathcal{I}$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$
\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^t \in \mathcal{I}_n$, (where $t=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
\[
|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^t)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^t)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^t|}) = 1] | < \frac{1}{p(n)} \enspace,
\]
where $(I^1,\dots,I^t)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
\end{enumerate}
\end{definition}
